A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-23 07_Manuscript.Rmd
Correct Rmd so that it knits

This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules which commenced 'late' were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease. 
Growers typically do not have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing. 
Also, weather conditions and logistical issues might prevent growers from getting machinery in the paddock to treat the disease immediately after it is spotted. 
These issues, and perhaps other on farm duties, might delay a timely application, permitting the disease more time to establish. 
Knowing a delay of up to two weeks may not lead to yield losses, can allow growers to incorporate other integrated pest management options, such as insecticide, with the fungicide spray saving on spray application costs. 
However attention should be made to the label requirements when first planning a spray schedule.
Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
If time permitted a second spray after the first 'late' application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10]`).

>>>>

This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules which commenced 'late' were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease. 
Growers typically do not have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing. 
Also, weather conditions and logistical issues might prevent growers from getting machinery in the paddock to treat the disease immediately after it is spotted. 
These issues, and perhaps other on farm duties, might delay a timely application, permitting the disease more time to establish. 
Knowing a delay of up to two weeks may not lead to yield losses, can allow growers to incorporate other integrated pest management options, such as insecticide, with the fungicide spray saving on spray application costs. 
However attention should be made to the label requirements when first planning a spray schedule.
Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
If time permitted a second spray after the first 'late' application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.
